OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2017-11-23 manuscript_nar.tex
Minor changes (need the commit to merge).

The originality of \textit{OneD} lies in the estimation of the explicit
biases and the copy number from a single variable: the contact profile.
This allows greater running speed, while preserving a good performance on
samples with karyotypic aberrations. One of the reasons why \textit{OneD}
is able to better highlight the biological distinctions between samples is
that it only corrects the copy number if specifically requested by the
user. The impact of copy number variations on normalization is rather
opaque, especially if they are treated as implicit biases
(Figure~\ref{fig:cnv_correction}B). Treating them as explicit biases with
optional removal seems to be an overall safer strategy. In homogeneous
data sets, correcting for the copy number can blur the biological signal,
but when karyotypes are variable or unstable, it may increase the
reproducibility (Figure~\ref{fig:cnv_correction}A).

>>>>

The originality of \textit{OneD} lies in the estimation from a single
variable of the explicit biases with a Negative Binomial model and of the
copy number. This allows greater running speed, while preserving a good
performance on samples with karyotypic aberrations. One of the reasons why
\textit{OneD} is able to better highlight the biological distinctions
between samples is that it only corrects the copy number if specifically
requested by the user. The impact of copy number variations on
normalization is rather opaque, especially if they are treated as implicit
biases (Figure~\ref{fig:cnv_correction}B). Treating them as explicit
biases with optional removal seems to be an overall safer strategy. In
homogeneous data sets, correcting for the copy number can blur the
biological signal, but when karyotypes are variable or unstable, it may
increase the reproducibility (Figure~\ref{fig:cnv_correction}A).
